---
title: "Textgrid Packages"
output: html_notebook
---

# Options

## `readtextgrid`

- url:https://github.com/tjmahr/readtextgrid
- pros
    - recently developed
    - built with tidyverse in mind
- cons
    - actually, it takes a looooong time to read these textgrids!
    - really really long?

```{r}
library(readtextgrid)
library(tidyverse)
```

```{r}
tg <- read_textgrid("../extdata/dod/dod.TextGrid")
```

```{r}
tg2 <- read_textgrid("../../aw_timewarping/1_data/0_audio_textgrid/PH06-2-1-AB-Jean.TextGrid")
```

```{r}
tg2
```


```{r}
tg
```

```{r}
words <- tg %>% filter(tier_name == "IVR - words") %>%
  rename(word_num = annotation_num,
         word_text = text)
phones <- tg %>% filter(tier_name == "IVR - phones") %>%
    rename(phone_num = annotation_num,
           phone_text = text)
```


```{r}
phones %>%
  left_join(words %>% select(xmin, word_text, word_num)) %>%
  fill(word_text, word_num)
```


## `rPraat`


- url: https://github.com/bbTomas/rPraat/
- pros
    - faster
- cons
    - will require more work to get to an acceptable dataframe. 

```{r}
library(rPraat)
library(tidyverse)
```

```{r}
tg <- tg.read("../../aw_timewarping/1_data/0_audio_textgrid/PH06-2-1-AB-Jean.TextGrid")
```

```{r}
tg %>% map(as.data.frame)
```


## `textgRid`
- url: https://github.com/patrickreidy/textgRid
- pros
    - faster
- cons
    - cran version broken, github version ~stable~ broken
    - difficult to get into dataframe!

```{r}
library(textgRid)
library(tidyverse)
```

```{r}
tg <- TextGrid("../extdata/dod/dod.TextGrid")
```

```{r}
str(tg$`IVR - words`)
```


# rPraat wins

## Doing it by hand

```{r}
library(rPraat)
library(tidyverse)
```

```{r}
tg <- tg.read("../../aw_timewarping/1_data/0_audio_textgrid/PH06-2-1-AB-Jean.TextGrid")
```

```{r}
tg %>%
  map_dfr(as.data.frame) %>%
  separate(name, into = c("speakerid", "type"), sep = "\\s+?-\\s+?") %>%
  group_by(speakerid, type) %>%
  mutate(n = 1:n()) %>%
  ungroup()-> tg_df
```

```{r}
phones_df <- tg_df %>% filter(grepl("phone", type)) %>%
                        rename(phone_label = label,
                               phone_n = n)
  
words_df <- tg_df %>% filter(grepl("word", type)) %>%
                        rename(word_label = label,
                               word_n = n)
```

```{r}
phones_df %>% 
  left_join(words_df %>% select(speakerid, t1, word_label, word_n)) %>%
  fill(word_label, word_n) -> structured
```

## Doing it with the package

```{r}
tg <- faver::read_textgrid("../extdata/dod/dod.TextGrid")
```
```{r}
faver::word_phone_nest(tg) %>% group_by(speakerid, word_n) %>% 
  nest()->word_nest
```


```{r}
word_nest$data[[6]]
```

